%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-2mm}
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Law firm} % Organization
    {BLOCKCHAIN, SOLUTIONS ARCHITECT \& SENIOR DEVELOPER} % Job Title
    {2020 – Present} % Dates
    {Bellevue, WA. USA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Technologies:} TS, Node, Solidity, Hardhat, ethers.js, Firebase, Docker, MongoDb, GCP, Twilio API, Sendgrid API, Figma
        \item Example Solidity contracts and tests: https://bit.ly/3gBr3Pr.
        \item Successfully delivered Ethereum Smart Contracts for Tokens, Sale, and its Distribution.
        \item Developed multi-signature contract library with mobile browser support using Svelte \& Firebase.
        \item Developed back-end APIs for communication with blockchain and smart contracts. 
        \item Implemented internal credit \& background research application using data feeds from the credit agencies.
        \item Subsequently negotiated and executed favorable licensing terms to client.
        \item Developed client management IVR and outbound voice-based questionnaire application.
        \item Authored system architecture, designed user interface, and lead team of engineers.
        \item Authored multiple forensic computer expert opinions for legal cases.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NVMI Blockchain \& PlatON.Network} % Organization
    {BLOCKCHAIN ARCHITECT} % Position
    {2019 – 2020} % Dates
    {Hong Kong, Hong Kong} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Technologies:} Go, Python, Bash, Docker, Solidity, LateX
        \item Successfully created \& implemented strategy for community support for ATON, PlatON’s token.
        \item Examined \& designed blocksizes for PlatOn PoS consensus algorithm.
        \item Conducted in depth analysis of leading consensus algorithms, hybrid PoS, and PoW blockchains.
        \item Managed the prototype of multi-party computation implementations on ARM64.
        \item Performed editing of all English website content, marketing, and investor materials, GitHub documentation.
        \item Participated in Ethereum Foundation joint development \& collaboration meetings.
        \item Evaluated \& delivered reports on PlatON whitepaper and economics paper.
        \item Gather, document, \& review industry white papers, smart contracts, and crowd funding schemes.
        \item Conducted code reviews with PlatON’s blockchain testnet in Python, Go, \& Docker-compose and identified key economic \& technical issues. And evaluated worldwide legal disclosures and reporting requirements.
        \item Analyzed \& contributed critical feedback for marketing, investor, and developer community materials.
        \item Authored numerous internal papers regarding architecture, design, cryptographic processing requirements.
        \item Presented to executive’s analysis of the Ethereum Platform architecture \& technologies.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {A DOT Corporation} % Company
    {SOLUTIONS ARCHITECT } % Position
    {2017 – 2018} % Date(s)
    {Bellevue, WA. USA} % Location
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Technologies:} C++, TS, C#, JS, SQL, Docker, Solidity, LateX
        \item Developed research \& reports for Northwest Venture firms evaluating investments in Ethereum, Bitcoin, and Blockchain.
        \item Contributed to macOS Artifact Parsing Forensic Software Tool.
        \item Negotiated ransomware settlement for Chinese manufacturer.
     \end{cvitems}
    }
  \vspace{-3mm}
  \cventry
    { } % Job title
    { } % Organization
    { } % Location
    { } % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed courtroom and deposition audio transcription system using AWS, Google ML.
        \item Developed court records ingest system for law office internal client management software.
        \item Developed law firm’s court/client tracking software and adversarial background search management web application.
        \item Developed smart contract templates for arbitrary bounty, consulting services.
        \item Developed iOS, Android application for consolidating location data for forensic analysis.
        \item Manufactured radio monitoring device for Microsoft Research.
        \item Developed digital audio, video compression, encryption, usage format for Secure Digital licensed by Toshiba Corporation.
    \end{cvitems}
    }
 
  \cventry
    {Playlist Licensing, LLC.} % Job title
    {DIRECTOR OF PATENT LICENSING} % Organization
    {2013 – 2017} % Location
    {Seattle, WA. USA} % Date(s)
    {
     \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Technologies:} C++, TS, JS, Node, Excel
        \item Monetized company’s intellectual property through licensing agreements. 
        \item Created internal work-flow for customer on-boarding and subsequent licensing of company’s patents. 
        \item Employed front-end and back-end e-commerce site for managing licenses. 
        \item Managed company’s legal activities. 
        \item Developed all corporate financial revenue modeling and legal budgets, achieving on budget quarterly reports to the board of directors.
        \item Developed an automated patent licensing scheme.
        \item Licensed Intellectual agreements of over \$5M revenue.
        \item Consulted with hardware manufactures to integrate embedded software.
        \item Designed and developed C++ source code for embedded digital media players.
        %\vspace{-3mm}
     \end{cvitems}
    }

  \vspace{-.5mm}
  \cventry
    {Microsoft Corporation } % Organization
    {SOFTWARE ARCHITECT } % Job title
    {1998 - 2012} % Date(s)
    {Bellevue, WA. USA} % Location
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{-3mm}
        \end{cvitems}
    }

  \vspace{-5.0mm}
  \cventry
    {Saltmine Creative} % Job title
    {SOFTWARE ENGINEER } % Organization
    {1996 – 1998} % Location
    {Bellevue, WA. USA} % Date(s)
    {
      \begin{cvitems} % Description(s) of 
        \vspace{-3mm}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
%---------------------------------------------------------
% Compact Projects
%---------------------------------------------------------
    \vspace{-3.0mm}
    \cventry
        { } 
        {PRODUCTS \& PROJECTS} 
        {2008 – 2021} 
        { } 
    {
      % \begin{cvitems} 
      % \end{cvitems}
    \vspace{-9mm}
      \begin{cvsubentries}
        \cvsubentry{}{ERC20, Token Sale, Hardhat TS}{https://bit.ly/3q6gA32}{}
        \cvsubentry{}{QR Code Reader/Generator Svelte Component}{https://bit.ly/3iFqA1s}{}
        \cvsubentry{}{Slushpool monitor xbar plugin}{https://bit.ly/3sNcxJq}{}
        \cvsubentry{}{FireDialer IVR Open Source}{https://bit.ly/2TF0Gk4}{}
        \cvsubentry{}{MEOW Token, OpenZeppelin}{https://bit.ly/2UelfUN}{}
        \cvsubentry{}{EcoCarCafe Customer Management System}{https://bit.ly/2TZaDZx}{}
        \cvsubentry{}{Natasha Pankina Illustrations}{https://bit.ly/3iJTRYJ}{}
        \cvsubentry{}{macOS Artifact Parsing Tool}{http://bit.ly/2QdfTTY}{}
        \cvsubentry{}{U.S. Security and Exchange Commission NLP Analysis}{https://bit.ly/2SvrW4k}{}
        \cvsubentry{}{GreenPlay Audio Video Format}{https://bit.ly/3cL4d6Q}{}
        \cvsubentry{}{Starbuck's Overhead Music and Hear Music Solution}{}{}
        \cvsubentry{}{MSN Direct Watch/Microsoft SPOT}{https://bit.ly/35pFSzx}{}
        \cvsubentry{}{Iomega Hipzip MP3 Player}{http://bit.ly/2Mjr0tp}{}
        \cvsubentry{}{Transworld Listening Viewing Sampling Station}{https://bit.ly/2Ub3CoL}{}
        \cvsubentry{}{Digital Audio Embedded Operating System}{http://bit.ly/2Mjr0tp}{}
        \cvsubentry{}{Fixed Point MPEG II Layer 3 Decoder}{https://bit.ly/3xp2qwb}{}
        \cvsubentry{}{Glove Grasp, Java SDK Gesture Recognition}{https://bit.ly/3voEJTv}{}
      \end{cvsubentries}
    }
%---------------------------------------------------------
\end{cventries}
\vspace{-1.5mm}